Stat 400 Project

### 2021-12-04 Stat 400 proj.Rmd
fix indexing for recovery df?

@@

#Function for deciding if infections occurred
#BUG -- If the mean_crit_dist is small, all infections go away!!
infection_status <- function(state, mean_crit_dist,t){

@@

  #is this right do get the list of recovery days?
  current_rec_time <- state[state[,4]]

@@

      z_s <- as.numeric(current_rec_time[i])

@@

      else{
        new_status[j] <- 'S'
      }
    }
  }

  current_non_infected[newly_infected, 3] <- 'I'
  new_state <- rbind(current_infected, current_non_infected)

  # new_state <- c(new_status, current_infected[,3])
  return(new_state)
}

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 2,i)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

@@

      new_status <- infection_status(updated_state, 2)

@@

      updated_positions <- update_coords(end_day[[i-1]], change)
      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 1/5,i)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

@@

      rand_recovery_time <- rpois(1,14)
      new_status <- infection_status(updated_state, 1/5,i,rand_recovery_time)

@@

#Testing
df <- starting_vals(100, 2, 10, 10)
len <- get_step_length(df, 10, 10)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 10, 10)
new_status <- infection_status(coords, 2)
new_status

>>>>

  #Create null incubation and recovery time columns
  #inc_time <- rep(NA, num_subjects)
  #rec_time <- rep(NA, num_subjects)

@@

#Function for deciding if infections occurred
#BUG -- If the mean_crit_dist is small, all infections go away!!

#t = the current day, rt is df of recovery times. 
infection_status <- function(state, mean_crit_dist,t,rt){

@@

@@

      #day of recovery for current infected
      z_s <- as.numeric(rt[i])

@@

      #else{
       # new_status[j] <- 'S'
      #}
    }
  }

  new_state <- rbind(current_infected, current_non_infected)
  return(new_state)
}

@@

      updated_positions <- update_coords(initial_data, change)
      checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 2,i,recovery_time)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

@@

      new_status <- infection_status(updated_state, 2,i,recovery_time)

@@

      updated_positions <- update_coords(end_day[[i-1]], change)
      checked_positions <- coord_checker(og_df=end_day[[i-1]], new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
      new_status <- infection_status(checked_positions, 1/5,i,recovery_time)
      checked_positions[,3] <- new_status
      end_day[[i]] <- checked_positions

@@

      rand_recovery_time <- rpois(1,14)
      new_status <- infection_status(updated_state, 1/5,i,recovery_time)

@@

#Testing
df <- starting_vals(100, 2, 10, 10)
len <- get_step_length(df, 10, 10)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 10, 10)
#new_status <- infection_status(coords, 2)
#new_status
